---
title: "Illustrative Analysis with Stochastic Interventional Effects"
author: "[Nima Hejazi](https://nimahejazi.org) and [Kara
  Rudolph](https://kararudolph.github.io/)"
date: '`r format(Sys.time(), "%Y %b %d (%a), %H:%M:%S")`'
output:
  pdf_document
---

First, let's load necessary packages and some utility functions:
```{r}
# load packages and helper files
library(here)
library(hal9001)
library(tidyverse)
library(SuperLearner)
source(here("R", "utils.R"))
set.seed(7518)
```

Now, let's load the data and take a quick look
```{r}
# set shift for incremental propensity score
delta_ipsi <- 2

# load permuted data from Kara
data <- read_csv(here("data", "xbot_permuted.csv"))
head(data)
```

Hmm, let's also take a look at the exposure (since we've been running into
bugs):
```{r}
# permutation bug: A is all zero for some reason?!
table(data$A)

# for now, let's just make up an exposure
data$A <- rbinom(nrow(data), 1, 0.6)
```

Somewhat inconveniently, we ended up loading a number of helper functions
related to our simulation code (when we ran (`source(here("R", "utils.R"))`).
To make sure these don't interfere with our debugging, let's go ahead and remove
everything but the bare minimum of helper functions and data:

```{r}
# remove extra stuff from utils.R
rm(list = setdiff(ls(), c("bound", "truncate", "gfun", "gdeltafun", "gdelta1",
                          "delta_ipsi", "data")))
```

With that out of the way, let's also load our Super Learning helper functions
and code for computing our efficient estimators of the (in)direct effects:

```{r}
source(here("R", "slfuns.R"))
source(here("R", "estimate.R"))
```

Now, let's set some Super Learning libraries. The dataset includes
`r ncol(data)` columns, which may pose a problem for using the highly adaptive
lasso. Luckily, none (?) of our theory actually relies on its $n^{-1/4}$
convergence rate, so we ought to be alright excluding it in a preliminary
analysis. Based on this, the library `sl_lib` below seems a reasonable choice:

```{r, message=FALSE, warning=FALSE}
# set up SL library + smaller library for faster debugging
sl_lib <- c("SL.mean", "SL.bayesglm", "SL.earth", "SL.gam", "SL.glmnet",
            "SL.caretXGB", "SL.caretRF")
sl_lib_with_hal <- c(sl_lib, c("SL.myglm", "SL.myglmnet", "SL.hal9001"))
sl_lib_debug <- c("SL.mean", "SL.bayesglm")
```

Alright, now we're ready to estimate nuisance parameters and construct our
estimators -- finally! Let's go ahead with that.

```{r}
# estimate nuisance parameters
nuisance <- fitnuisance(data, nfolds = 5, sl_lib = sl_lib_debug)

# construct estimates of (in)direct effects
out <- estimators(data, delta = delta_ipsi, nuisance, sl_lib = sl_lib_debug)
out
```

Reassuringly, the output above seems to indicate pretty good agreement between
the one-step and TML estimators of the (in)direct effects.

In case we run into reproducibility issues, let's check the R session info:

```{r}
sessioninfo::session_info()
```
